\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Zachary Taira}

\section{Work experience}

\begin{eventlist}

\item{Jan -- July 2016}
     {Resilient, an IBM Company}
     {Sales Engineer}

Built custom modules for current and prospective Resilient customers using
Python. Team lead on building out Sales Engineering demo environment,
ensuring its reliability, and demoing new functionality for Account Executives.
Created Resilient API Examples GitLab repository to store and showcase
said Python integrations. Ran meetings to keep the Sales Engineering
team up to date.

\item{Jan 2015 -- Jan 2016}
     {Northeastern SMILE Lab}
     {Undergraduate Research Assistant}

Led a team of 9 students in creating a familial image database for image
reconition by organizing data collection deadlines and scheduling meetings.
Personally contributed over 1500 out of 6000 total images. Parsed through and
compiled statistics for the database using Python. 

\item{May -- Sept 2015}
     {Northeastern University}
     {Orientation Leader}

Worked efficiently alongside a team of 35 peers and graduate students to
foster an atmosphere of inclusivity and support for new students and their
families over 3-day orientation cycles. Led numerous icebreakers and team
bonding activities for 5 unique 20-person student groups and 2800 university
guests. Volunteered cheerfully to help staff undermanned activites.
\end{eventlist}

\section{Relevant Coursework}
\begin{factlist}
\item{2016}
    {Fundamentals of Linear Systems\\
    Fundamentals of Electronics\\
    Fundamentals of Networks\\
    Advanced Writing}
\item{2015}
    {Linear Algebra/Differential Equations\\
    Circuits and Signals\\
    Probability and Statistics\\
    Embedded Design\\
    Engineering Mechanics and Design\\
    Engineering Problem Solving and Computation}
\item{2014}
    {Calculus 3\\
    Engineering Design}
\end{factlist}

\personal
    {zach.taira@gmail.com}
    {(808)-238-9713}
    {github.com/ztaira14}
    {www.linkedin.com/in/zacharytaira}

\section{Projects (On GitHub)}

\begin{yearlist}

\item{Oct 2016}
    {hub\_where (Python)}
    {Hack-A-Week 11 and 12: Python scripts to gather and visualize data
from Hubway's bike-sharing stations}

\item{Sept 2016}
    {evil\_maid\_suite (Python)}
    {Hack-A-Week 10: Data Visualization on the time I keylogged myself}

\item{Aug 2016}
    {uku\_tabs (C++)}
    {Hack-A-Week 6 and 7: A terminal-based guitar/ukulele tab management tool}

\item{July 2016}
    {flappy\_term (C++)}
    {Hack-A-Week 4: ASCII flappy bird clone using ncurses}

\item{July 2016}
    {python\_flow (C++)}
    {Hack-A-Week 2: A python flow visualizer in C++}

\item{July 2016}
    {aes\_python (Python)}
    {Hack-A-Week 1: An attempt at implementing the Advanced Encryption
    Standard in Python}

\end{yearlist}

\section{Education}

\begin{yearlist}

\item[B.S. in Electrical Engineering \newline GPA: 3.65, Dean's List]{May 2019}
     {Northeastern University}
     {Boston, MA}

\item{May 2014}
     {Punahou School}
     {Honolulu, HI}

\end{yearlist}

\section{Software skills}

\begin{factlist}

\item{Languages:}
     {Python, C++, bash, MATLAB, HTML, CSS, Javascript, SQLite, Vimscript, LaTeX}

\item{Operating Systems:}
     {Linux, Mac OS X}

\item{Technologies:}
     {git, Resilient, Solidworks, PSpice}

\end{factlist}

\end{document}
